% ----------------------------------------------------------------------------------------
% SECTION TITLE
% ----------------------------------------------------------------------------------------

\cvsection{Projects}

% ----------------------------------------------------------------------------------------
% SECTION CONTENT
% ----------------------------------------------------------------------------------------

\begin{cventries}

  % ------------------------------------------------
  \cventry
  {Dean of Research and Development,IITK}
  {{\entrytitlestyle{HURO}}
    {}}
  {IIT Kanpur}
  {December 2016-Present}
  {
    \begin{cvitems}
    \item Used OpenCV(C++) to achieve  tasks such as Line Following,Face Detection,Object Detection and Object tracking.
    \item Implemented an algorithm to detect and tell the direction of arrow placed on the ground.
    \item Used OpenCV(Python) for feature detection in images.
    \item Worked on voice localisation,which makes use of four mics and Arduino to tell the direction of the sound source.
    \item Used Arduino to take the input and did the processing using Python.
    \end{cvitems}
    \vspace{-5mm}
  }
  \cventry
  {Programming Club,IIT Kanpur}
  {Battleship Gaming AI}
  {IIT Kanpur}
  {May 2016 - June 2016}
  {
    \begin{cvitems}
      \item Developed a gaming AI using Python which can play the Battleship game.
      \item Implemented it using Probabilistic methods as well as using Machine Learning.
      \item Implemented the Machine Learning part using Neural Networks.
      \item Made a GUI for the game using the pygame module of python.
    \end{cvitems}
  }
  \cventry
  {}
  {{\entrytitlestyle{Microsoft Code.Fun.Do}}}
  {IIT Kanpur}
  {March-2017}
  {
    \begin{cvitems}
    \item Developed a Windows game as a part of the seven days hackathon.
    \end{cvitems}
  }
  % ------------------------------------------------
\end{cventries}

%%% Local Variables:
%%% mode: xelatex
%%% TeX-master: "../resume_twopage"
%%% End:
